\chapter{Forecast Results}
\label{chapter:results}

\section{Final Quantile Predictions}
\label{sec:final_predictions}

Table~\ref{tab:target_forecasts} presents the 5th, 50th, and 95th percentiles of the optimized Decision Maker for the four target variables. These are subjective uncertainty quantiles, not frequentist confidence limits.

\begin{table}[htbp]
    \centering
    \begin{tabular}{lrrr}
        \toprule
        \textbf{Target variable} & $\boldsymbol{q_{0.05}}$ & $\boldsymbol{q_{0.50}}$ & $\boldsymbol{q_{0.95}}$ \\
        \midrule
        Completed dwellings & \DwellingsFive{} & \DwellingsMedian{} & \DwellingsNinetyFive{} \\
        Residential building permits & \PermitsFive{} & \PermitsMedian{} & \PermitsNinetyFive{} \\
        Amsterdam transaction price (\euro) & \PriceFive{} & \PriceMedian{} & \PriceNinetyFive{} \\
        Free-sector rent growth (\%) & \RentFive{} & \RentMedian{} & \RentNinetyFive{} \\
        \bottomrule
    \end{tabular}
    \caption{Optimized Decision Maker forecasts for 2027.}
    \label{tab:target_forecasts}
\end{table}

The optimized distribution places the median number of completed dwellings at \DwellingsMedian{}, with a central 90\% interval from \DwellingsFive{} to \DwellingsNinetyFive{}. The corresponding permit forecast has a median of \PermitsMedian{} and an interval from \PermitsFive{} to \PermitsNinetyFive{}. The Amsterdam transaction-price median is \euro\PriceMedian, while the median forecast for free-sector rent growth is \RentMedian\%.

\section{Narrative Interpretation}
\label{sec:narrative_interpretation}

The completed-dwellings forecast is the clearest policy result. Its median is approximately 25\% below the government's ambition of 100,000 dwellings per year, and even the 95th percentile remains below that benchmark. Conditional on this panel and model specification, reaching 100,000 completed dwellings in 2027 is therefore assigned little probability.

Building permits measure the future pipeline rather than completed supply, so the two forecasts should not be compared one-for-one. Nevertheless, a permit median of \PermitsMedian{} does not indicate the acceleration required to remove the existing shortage quickly. The supply forecasts are consistent with the constraints identified in Chapter~1: long approval periods, labour scarcity, financing pressure, and nitrogen-related restrictions.

The price and rent forecasts describe the affordability consequences of continued scarcity. The optimized median transaction price in Amsterdam is \euro\PriceMedian, with a broad interval that reflects uncertainty about financing conditions and local demand. Free-sector rent growth remains positive throughout the central 90\% interval. These results do not identify the causal contribution of any single policy; they summarize the panel's joint uncertainty about market outcomes.
