\chapter{Expert Elicitation Instrument and Protocol}
\label{appendix:elicitation_protocol}

This appendix presents the complete collection of elicitation questions utilized in this Structured Expert Judgment study. Section~\ref{app:sec_calibration} documents the ten historical calibration (seed) variables alongside their exact empirical realizations and source tracking. Section~\ref{app:sec_targets} outlines the four forward-looking target parameters designed to model the 2027 Dutch residential landscape. All variables require experts to specify their subjective uncertainty via the 5\%, 50\% (median), and 95\% quantiles.

\section{Calibration Questions (Seed Variables)}
\label{app:sec_calibration}

\subsection*{Calibration Question 1: Existing Owner-Occupied Transaction Prices}
Given that the average transaction price of an existing owner-occupied dwelling in the Netherlands was €416,000 in 2023, what was the average transaction price (in Euros) for the entire calendar year of 2025?\\\newline
\textbf{True Realization:} €480,000\\\newline
\textbf{Source Document:} \textit{Centraal Bureau voor de Statistiek} (CBS), 2026.

\subsection*{Calibration Question 2: Outstanding Residential Mortgage Debt}
What was the total outstanding residential mortgage debt held by Dutch households (in billions of Euros) at the end of 2025?\\\newline
\textbf{True Realization:} €890.171 Billion\\\newline
\textbf{Source Document:} De Nederlandsche Bank (DNB) Mortgage Market Statistics, 2025.

\subsection*{Calibration Question 3: Net National Population Growth}
Given that net population growth in the Netherlands was 220,619 persons in 2022, what was the net population growth, defined as (births + immigration) minus (deaths + emigration), in 2025?\\\newline
\textbf{True Realization:} 87,211 Persons\\\newline
\textbf{Source Document:} CBS Population Dashboard, 2026.

\subsection*{Calibration Question 4: Absolute National Housing Inventory}
By the end of 2024, how many dwellings were there in the Netherlands in total?\\\newline
\textbf{True Realization:} 8,274,478 Dwellings\\\newline
\textbf{Source Document:} CBS, \textit{Basisregistratie Adressen en Gebouwen} (BAG), 2025.

\subsection*{Calibration Question 5: Rental Property Sector Proportions}
Given that 42.7\% of all dwellings in the Netherlands were rental properties in 2021, what percentage of all dwellings were rental properties (both social and free-sector) by the end of 2024?\\\newline
\textbf{True Realization:} 42.4\%\\\newline
\textbf{Source Document:} CBS, BAG, 2025.

\subsection*{Calibration Question 6: Existing Market Transaction Volumes}
How many total existing home sales transactions took place in the Netherlands in the first quarter of 2026 (January–March 2026)?\\\newline
\textbf{True Realization:} 34,579 Transactions\\\newline
\textbf{Source Document:} \textit{Nederlandse Vereniging van Makelaars} (NVM) Quarterly Market Report, 2026.

\subsection*{Calibration Question 7: One-Person Household Demographics}
Given that 17.7\% of the population of the Netherlands lived in a one-person household at the beginning of 2020, what percentage lived in a one-person household at the beginning of 2025?\\\newline
\textbf{True Realization:} 19\%\\\newline
\textbf{Source Document:} CBS Bevolkingsdashboard (Huishoudens), 2025.

\subsection*{Calibration Question 8: International Higher Education Enrollment}
In the academic year 2025–2026, how many foreign (international) students were enrolled in Dutch higher education institutions?\\\newline
\textbf{True Realization:} 91,660 Students\\\newline
\textbf{Source Document:} CBS Open Data Repository, Table 85125NED, 2026.

\subsection*{Calibration Question 9: Average Rent-to-Income Expenditure Ratios}
Given that net rental price represented 25.3\% of net income for Dutch renters on average in 2018, what percentage of net income did the net rental price (gross rent minus rent allowance) represent on average in 2024?\\\newline
\textbf{True Realization:} 24.7\%\\\newline
\textbf{Source Document:} \textit{Woononderzoek Nederland} (WoON) Survey, 2024.

\subsection*{Calibration Question 10: Estimated Homeless Population Indices}
How many homeless people were there in the Netherlands in 2024 (CBS estimate at start of year)?\\\newline
\textbf{True Realization:} 23,600 Persons\\\newline
\textbf{Source Document:} CBS, May 2025 Release.

\section{Target Questions (Predictive Variables of Interest)}
\label{app:sec_targets}

The following queries represent the core target variables elicited from the expert panel to formulate the optimized performance-weighted forecasts for the 2027 housing sector:

\subsection*{Target Question 1: Realized Volume of New Dwellings}
What will be the total number of newly completed dwellings realized in the Netherlands during the entire calendar year of 2027?

\subsection*{Target Question 2: Municipal Residential Building Permits}
How many total residential building permits will be formally issued in the Netherlands during the calendar year of 2027?

\subsection*{Target Question 3: Affordability Scaling in Municipal Amsterdam}
What will be the average selling price (in Euros) of an existing owner-occupied home within the municipal boundaries of Amsterdam for the entire calendar year of 2027?

\subsection*{Target Question 4: Free-Sector Rent Escalation Coefficients}
What will be the percentage increase in average rent for free-sector rental properties (\textit{vrijesectorwoningen}) across the Netherlands as of July 1, 2027, relative to the baseline index on July 1, 2026?